\documentclass[12pt,english]{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{courier}
\usepackage{verbatim}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{setspace}
%\usepackage{esint}
\onehalfspacing
\usepackage{babel}
\usepackage{amsmath}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\begin{document}

\title{Notes for Balasubramaniam \& Sakakibara 2015, ``Human Capital of Spinouts''}
\author{Nicolas Fernandez-Arias}
\maketitle

\begin{itemize}
	\item Identify spinouts using LEHD / LBD, methodology similar to Muendler
	\item Consider how founder characteristics -- specifically those relating to human capital -- determine the performance of spinouts
	\item Find what you'd expect: more experience in the industry, higher wages at the previous employer in the industry, etc. all lead to more successful spinouts
	\item Consistent with my learning story. Moments that can be matched.
	\item \textbf{Interesting finding:} Age predicts less ``successful'' spinouts by their measures.
	\begin{itemize}
		\item This is controlling for experience and other forms of human capital
		\item Suggests an age effect, not only on LIKELIHOOD of becoming an entrepreneur, but on the PATH that entrepreneurship takes in the event that it occurs
		\item I don't THINK Niklas Engbom studies this - I kind of want to ask him...
	\end{itemize}
	\item \textbf{What I want to do:} Similar analysis, but:
	\begin{itemize}
		\item Link with patent and R\&D data, to see whether incumbent R\&D / patents / innovation etc. leads to more / more successful spinouts
		\item Look at higher granularity industries - 1-digit SIC is much too broad (maybe small sample size problem...)
		\item Using VentureSource --> can get previous occupation and potentially better measures of spinouts. Occupation provides better measure of human capital. 
		\item Using Brazilian data instead of LEHD (which is insanely hard to access..) --> previous occupation. Maybe this is the move, if I'm studying spinouts.
		\item If I have LEHD, 
	\end{itemize}
\end{itemize}




\end{document}