\documentclass[12pt,english]{article}
%\usepackage{lmodern}
\linespread{1.05}
\usepackage{mathpazo}
%\usepackage{mathptmx}
%\usepackage{utopia}
\usepackage{microtype}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[dvipsnames]{xcolor}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsfonts}

\usepackage{courier}
\usepackage{verbatim}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}


\definecolor{red1}{RGB}{128,0,0}
%\geometry{verbose,tmargin=1.25in,bmargin=1.25in,lmargin=1.25in,rmargin=1.25in}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{setspace}

\usepackage[colorlinks=true, linkcolor={red!70!black}, citecolor={blue!50!black}, urlcolor={blue!80!black}]{hyperref}
%\usepackage{esint}
\onehalfspacing
\usepackage{babel}
\usepackage{amsmath}
\usepackage{graphicx}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\begin{document}
	
	
	
\title{Endogenous Growth with Spinouts - Empirical Component}
\author{Nicolas Fernandez-Arias}
\maketitle

\section*{To-do}

\begin{enumerate}
	\item ONLY CONTROL EMPLOYment - everything else too correlated with R\&D 
	\item firm patents --> shock to firm R\&D spending 
	\item use other measures of R\&D (patents)
	\item non-competes affect incentive to do R\&D, but non-competes don't affect difference ..think about this (can maybe look at industry level)
	\item two approaches: (1) find basic effects of model in data, (2) run regressions in model and data (so just a moment you can use, so specification doesn't matter)
	\item Talk to some empirical people about the "right" way to do this
	\item FIGURE OUT HOW GOOD YOUR MATCH IS
	\item REPLICATE GOMPERS LERNER SCHARFSTEIN (Just replicate the tables)
	\item Cross-walk - make sure the codes aren't related to SIC or something...how did GLS do it??
	\item Regressions look interesting -- but would be better to look at outcomes of spinouts besides just spinout counts, and see how these are related to firm R\&D
	\item Re: potential spinouts vs. spinouts, can compare 1st funding to 2nd or 3rd funding, and how likelihood changes depending on when parent firm gets a patent. This is particularly powerful if most spinouts end up getting *some* funding (otherwise they wouldn't have spun out)
	\item Is there any better info in Compustat than just R\&D spending? I.e. R\&D employment? Some measure of high skill employment...(doesn't look like it...)
\end{enumerate}

\section*{Questions}

\begin{enumerate}
	\item Statistical / economic significance of preliminary results and what this says about feasiblity of IV approach...
	\item Cross-walk of industry codes - how to assess its quality?
	\item What controls would be appropriate? E.g., patent stock control? 
	\item Spinout formation in model and data:
	\begin{itemize}
		\item Model: potential spinouts vs. actual spinouts
		\item Data:
		\begin{itemize}
			\item Founding of a startup --> potential spinout
			\item Raising certain amount of money, or generating revenue (when have data) --> discovery of new variety by a spinout?
		\end{itemize}
	\end{itemize}
	\item Non-constant hazard rate:
	\begin{itemize}
		\item When parent firm obtains a patent, the likelihood of a spinout raising money drops, whereas the likelihood of generating new potential spinouts increases. This I could test in the data...
		\item \textbf{Problem:} I only observe founded firms that end up raising VC money. If a parent firm outcompetes its spinouts in the innovation race, then its spinouts will simply be less likely to appear in the dataset at all.  
	\end{itemize}
\end{enumerate}

\section*{Agenda}

\begin{enumerate}
	\item \textbf{(Significant progress)} Link startups in Venture Source to parent firms in Compustat
	\begin{itemize}
		\item \textbf{(done)} Parse employment biographies in Venture Source to extract previous employer 
		\item \textbf{(done)}) Match parent firms and subsidiaries using Compustat segments database (e.g., Google is a subsidiary of Alphabet, Inc.) 
		\item \textbf{(done)} Link previous employer to Compustat by matching (cleaned) name of company 
		\item \textbf{(in progress)} Get more matches by searching Google for "<company name> ticker symbol" and scraping results. Thousands of searches --> need Serp API (trial version for now) to use bots to scrape. So far have gotten about 10\% more matches this way. 
		\begin{itemize}
			\item \textbf{Issue: } most spinouts are from parents whose name is only associated with one or two spinouts (perhaps due to misspellings).
			\item \textbf{Issue: } there are false positives. But this should be relatively easy to fix, since there aren't too many matches. I can check by hand. There seem to be fewer false negatives.
		\end{itemize} 
		\item \textbf{(to-do)} Need to check matches for false positives. Measurement error on the LHS so still consistent, but lower power. 
		\item \textbf{(in progress)} 
		\item \textbf{(to-do)} Want to compare the counts of my approach to what is obtained by Gompers, Lerner and Scharfstein 2005, which uses the same datasets (for an earlier time period). 
	\end{itemize}
	\item \textbf{(to-do)} Construct industry code cross-walk linking NAICS4 and Venture Source industry categories
	\item \textbf{(to-do)} Construct instrument for R\&D spending using idiosyncratic component of Federal tax subsidies
	\begin{itemize}
		\item \textbf{Issue: } Results are already barely significant with firm, firm age and time fixed effects. Just not enough variation in R\&D spending. 
		\item \textbf{Issue: } Not sure have enough data on spinouts during the time period when the relevant Federal R\&D tax subsidies were put into place
	\end{itemize}
	\item \textbf{(to-do)} Construct database linking funding events (amounts, pre- and post- valuations) to daily stock prices (from CRSP)
	\item \textbf{(in progress)} Run regressions of spinout formation on R\&D spending
	\begin{itemize}
		\item OLS using all variation - i.e., no fixed effects
		\begin{itemize}
			\item Specifications: simultaneous, lagging moving averages of R\&D vs leading moving averages of spinout formation, etc.
			\item Relationship between R\&D and spinout formation seems to be more simultaneous (of course, only yearly data. So maybe happening at quarterly frequency or something).
		\end{itemize}
		\item OLS with some fixed effects
		\begin{itemize}
			\item More conservative clustering choices render insignificant
		\end{itemize}
	\end{itemize}
\end{enumerate}

\section{Empirical specification}

Throughout, the subscripts refer to firm $i$ in industry $j$ in state $s$ during year $t$. 

\subsection{Link between R\&D spending and spinout formation}
 
Assess the link between R\&D spending and spinout formation as follows:
\begin{align*}
	y_{ijst} &= \alpha_{jt} + \sigma_{st} + \beta RD_{it} + \gamma X_{it} + \epsilon_{ijst}
\end{align*}

\subsection{Effect of non-competes}

\subsubsection{Jeffers' specification}

First, we can assess the effect of non-competes on spinout formation generally -- the specification in Jeffers' paper on CNCs and spinouts: 
\begin{align*}
	y_{ijst} &= \alpha + \beta(treated_s \times post_{st}) + \gamma_i + \theta_{jt} + \epsilon_{ijst} 
\end{align*}

This might work. 

\subsubsection{Effect on R\&D --> spinout link}


\section{Important regressions}

\input{../tables/all_spinoutCount_regressions.tex}
\linebreak

\input{../tables/all_exitingSpinoutCount_regressions.tex}
\linebreak

\input{../tables/spinoutsDEV_firm-naicsyear.tex}

\subsection{With Jeffers court rulings}

\input{../tables/all_spinoutCount_regressions_JeffersCourtRulings.tex}
\linebreak
\input{../tables/all_spinoutDEV_regressions_JeffersCourtRulings.tex}



\subsection{With NCC enforcement index from Starr 2018 (1991 index)}

\input{../tables/all_spinoutCount_regressions_NCC1991-Starr2018.tex}

\subsection{Jeffers replication (kind of)}

\input{../tables/noPredictors_spinoutCount_regressions_JeffersCourtRulings.tex}

\subsection{Raw spinout count}

\input{../tables/rawSpinoutCount_firmFE.tex}
\linebreak

\subsection{Raw spinout count: negative binomial fixed effects regression}

\input{../tables/xtnbreg_rawSpinoutCount_firmFE.tex}
\linebreak

\subsection{Neg. bin., no FE}

\input{../tables/nbreg_rawSpinoutCount_firmFE.tex}
\linebreak

\subsection{Raw spinout count: poisson regression}

\input{../tables/xtpoisson_rawSpinoutCount_firmFE.tex}
\linebreak

\subsection{poisson regression, state dummies}

\input{../tables/poisson_rawSpinoutCount_stateFE.tex}
\linebreak

\subsection{Spinout DEV}

\input{../tables/SpinoutDEV_allFixedEffects.tex}
\linebreak


\section{No fixed effects}



\subsubsection{OLS}
\input{../tables/OLS.tex}
\linebreak
\input{../tables/patents_OLS.tex}
\linebreak
\input{../tables/patents-xrd_OLS.tex}
\linebreak
\input{../tables/patents-xrd_OLS_FE_industry3.tex}
\linebreak
\input{../tables/patents-xrd_OLS_FE_industry4.tex}
\linebreak
\input{../tables/patentsma3-xrdma3_OLS_FE_industry4.tex}
\linebreak
\input{../tables/patentsma3-xrdma3_OLS_DEV_FE_industry4.tex}
\linebreak
\input{../tables/patents-xrd_OLS_DEV_FE_industry4.tex}
\linebreak
\input{../tables/patentsma3-xrd_OLS_FE_industry4.tex}
\linebreak
\input{../tables/patentsma3-xrd_OLS_DEV_FE_industry4.tex}

\subsubsection{Logit}
\input{../tables/logit.tex}
\linebreak
\input{../tables/logit_exitsOnly.tex}
\linebreak
\input{../tables/logit_valuableOnly.tex}

\subsection{Dep var: discounted exit value of spinouts}

\input{../tables/OLS_discountedExitValue.tex} 

\section{No fixed effects with some additional controls}

\subsection{Dep var: spinout count weighted by \# of founders}

\input{../tables/OLS_more-controls.tex}

\subsection{Dep var: discounted exit value of spinouts}

\input{../tables/OLS_discountedExitValue_more-controls.tex}

\section{Fixed effects}

\subsection{Simultaneous R\&D}

\subsubsection{Spinout count}

\input{../tables/OLS_FE_industry2_age_time.tex}
\linebreak
\input{../tables/OLS_FE_industry3_age_time.tex}
\linebreak
\input{../tables/OLS_FE_industry4_age_time.tex}


\subsubsection{Discounted exit value Spinout count}
\input{../tables/OLS_DEV_FE_industry2_age_time.tex}
\linebreak
\input{../tables/OLS_DEV_FE_industry3_age_time.tex}
\linebreak
\input{../tables/OLS_DEV_FE_industry4_age_time.tex}

\subsection{3-year MA of R\&D}

\subsubsection{Spinout count}

\input{../tables/OLS_XRDMA3_FE_industry2_age_time.tex}
\linebreak
\input{../tables/OLS_XRDMA3_FE_industry3_age_time.tex}
\linebreak
\input{../tables/OLS_XRDMA3_FE_industry4_age_time.tex}


\subsubsection{Discounted exit value Spinout count}

\input{../tables/OLS_XRDMA3_DEV_FE_industry2_age_time.tex}
\linebreak
\input{../tables/OLS_XRDMA3_DEV_FE_industry3_age_time.tex}
\linebreak
\input{../tables/OLS_XRDMA3_DEV_FE_industry4_age_time.tex}


\end{document}
