\documentclass[12pt,english]{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{courier}
\usepackage{verbatim}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{setspace}
%\usepackage{esint}
\onehalfspacing
\usepackage{babel}
\usepackage{amsmath}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\begin{document}
	
\title{Extending spinouts model to non-competes}
\author{Nicolas Fernandez-Arias}
\maketitle

\section{Key issues}

\begin{enumerate}
	\item Economic
	\begin{enumerate}
		\item What happens to the idea if it is not spun out? Important in any case.
		\item Why non-competes are used just as frequently in places that do not enforce? Can we find any data that could help explain why? E.g., are these "useless" non-competes more common for employees of companies which have offices in enforcing states? If so this suggests it's just there for no reason...although we can also look into whether workers who have these are more or less mobile. 
		\item Why deleterious effects of non-competes arise from non-consideration? I.e., (1) states where consideration is not required, and (2) situations in which a non-compete is only presented after the job offer is accepted and the bargaining position is worse? Doesn't this suggest we should only use those cases as legitimate evidence against non-competes?
	\end{enumerate}
	\item Modeling
	\begin{enumerate}
		\item Non-permanent non-competes: each incumbent would have to keep track of all of the employees out there who are waiting for their non-competes to expire. Note that Shi gets around this by having each firm have only one employee, but that doesn't really make sense in my application.
		\item Multi-product firms: how to think about non-competes in this context? Competition now does not completely destroy an incumbent, but rather a product. One might argue it costs money to enforce. Now I have a little model that can explain some stuff...idk..
	\end{enumerate}
\end{enumerate}




\end{document}