\documentclass[12pt,english]{article}
\usepackage{palatino}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{courier}
\usepackage{verbatim}
\geometry{verbose,tmargin=0in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{setspace}
%\usepackage{esint}
\onehalfspacing
\usepackage{babel}
\usepackage{amsmath}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\begin{document}
	
\title{Questions for Ufuk Akcigit 2-12-2019}
\author{Nicolas Fernandez-Arias}
\maketitle

\begin{enumerate}
	\item Mechanism
	\begin{enumerate}
		\item R\&D $\to$ spinouts hypothesized due to tractability (firm's output problem is static) and realism (workers who innovate are more likely to form innovative companies). Makes sense?
	\end{enumerate}
	\item Identification
	\begin{enumerate}
		\item Which spinouts are creatively destroying and how much: in model WSOs destroy incumbent value. But within-industry spinouts do not completely steal from their incumbents. Which ones steal? How much do they steal? Funding dates impact on incumbent stock market values? 
		\item Patent data for identifying spinouts which are based on parent firm ideas
		\item Pre- and post-race spinouts in the data: there are two kinds of spinouts in the model - those that are doing R\&D in hopes of getting a product, and those that have successfully discovered a product. Which are which in the data? Is it fair to assume that at founding date, a spinout is in the former stage, and when it has revenue, it is in the latter stage?
		\item Causal effect of R\&D on spinout formation:
		\begin{itemize}
			\item Use of firm-specific federal tax incentive based on firm-specific base
			\item Use of state-level incentive - no longer firm-specific, ways around exclusion restriction.
		\end{itemize} 
	\end{enumerate}
	\item Model
	\begin{enumerate}
		\item No worker-entrepreneurship choice because no stationary $q/Q$ distribution, just stationary $E[q/Q|m]$. Seemingly no way to avoid. Big deal?
		\item Modeling of spinouts as drawing from different pool vs. same pool as incumbents. 
		\item Entrant \& spinout innovation production technology: DRS vs. CRS?
	\end{enumerate}
\end{enumerate}







\end{document}