\documentclass[12pt,english]{article}
\usepackage{lmodern}
\linespread{1.05}
%\usepackage{mathpazo}
%\usepackage{mathptmx}
%\usepackage{utopia}
\usepackage{microtype}
\usepackage{placeins}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[dvipsnames]{xcolor}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{svg}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{blindtext}
%\renewcommand{\arraystretch}{1.2}
\usepackage{multirow}
\usepackage{float}

% TikZ stuff

\usepackage{tikz}
\usepackage{mathdots}
\usepackage{yhmath}
\usepackage{cancel}
\usepackage{color}
\usepackage{siunitx}
\usepackage{array}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{tabularx}
\usetikzlibrary{fadings}
\usetikzlibrary{patterns}
\usetikzlibrary{shadows.blur}






%\usepackage{caption}
%\captionsetup{justification=raggedright,singlelinecheck=false}

\usepackage{courier}
\usepackage{verbatim}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}

\definecolor{red1}{RGB}{128,0,0}
%\geometry{verbose,tmargin=1.25in,bmargin=1.25in,lmargin=1.25in,rmargin=1.25in}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{setspace}

\usepackage[colorlinks=true, linkcolor={red!70!black}, citecolor={blue!50!black}, urlcolor={blue!80!black}]{hyperref}
%\usepackage{esint}
\onehalfspacing
\usepackage{babel}
\usepackage{amsmath}
\usepackage{graphicx}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\begin{document}
	
\title{Questions 12-10}
\author{Nicolas Fernandez-Arias}
\maketitle


\begin{enumerate}
	\item Non-competes important because value of knowledge to workers is lower than cost to firms. Driven by some combination of:
	\begin{itemize}
		\item Spinout idea production not very elastic to value of spinout ideas (e.g. because these are ideas which occur as a by-product of doing R\&D, not due to intentional research)
		\item Spinout idea implementation not very elastic to average value of spinouts (e.g. because new ideas tend to earn information rents, so marginally reducing their value only precludes a few low-rent ideas from ocurring, leaving the majority of high-rent ideas.)
		\item This all relies on parameter $\kappa$, which reduces new firm entry and spinout formation holding constant their productivity at R\&D (i.e., patents per R\&D employee). But I don't observe this.
		\item How to discipline $\kappa$ parameter?
	\end{itemize}
	\item For same reason, difficult to separately identify $\chi_S$ and $\nu$: both affect spinout entry, the only difference being that $\chi_S$ also affect spinouts patents per employee. But don't observe. Luckily, it seems that for my comparative static, it is sufficient to identify $(\chi_S - \chi_E)\nu$, which I can do without R\&D efficiency data.
	\item \textbf{Identfiying WSOs vs non-WSOs: }NAICS codes are incredibly broad. Don't have any better measure of product competition. 
	\item 
\end{enumerate}









\end{document}