\documentclass[7pt,english]{article}
\usepackage{lmodern}
%\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{verbatim}
\usepackage{booktabs}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=0.25in,rmargin=0.25in}
\usepackage{setspace}
%\usepackage{esint}
\onehalfspacing
\usepackage{babel}
\usepackage{amsmath}
\usepackage{lscape}
\begin{document}

\title{Aggregate empirical analysis}
\author{Nicolas Fernandez-Arias}
\maketitle

Try switching LHS and RHS
Need to think very carefully about exactly how to do this
Everything is endogenous
State-time specific Non-compete enforcement 

\section{Data sources}

\begin{enumerate}
	\item Total R\&D by state from NSF data
	\begin{itemize}
		\item location: Data/rd-by-state.dta
		\item Starts around 1991 for most states, from NSF National Patterns of R\&D resources
		\item Available in aggregated form and with entire history here https://www.nsf.gov/statistics/state-indicators/indicator/rd-performance-to-state-gdp/map (although in \% GDP terms, where I got must have used this + data on statelevel GDP by year, which is easy to find)
	\end{itemize}
	\item Private R\&D by state from NSF date (same source as above, see README)
	\item Census Business Dynamics Statistics on new business formation / employment by state and year
	\begin{itemize}
		\item ``Raw data'' location: Data/bds\_f\_agest.dta
		\item ``modified data'' location: Data/entry\_rates\_by\_state.dta
		\item Easy to find online I think...
	\end{itemize}
	\item Effective R\&D user cost of capital by state and year, from Bloom et al.
	\begin{itemize}
		\item ``Raw data'' location: Data/RDusercost\_2017\_13.dta
	\end{itemize}
\end{enumerate}

Also have IRIS data by state and industry pair. This could be interesting to look at if I have time. Needs to be cleaned, though, so no time probably. Also, no startup rates at state-industry level. 

\section{Notes}
\begin{enumerate}
	\item DONE - do it in logs - this made the signs look more like what I was expecting! Now there is a positive effect of R\&D spending on entry and job creation by new establishments / firms, respectively. 
	\item DONE - Normalize variables (before taking logs) - always good to do this, if it makes sense 
	\begin{itemize}
		\item Normalize R\&D spending by state GDP - easy
		\item Normalize establishment entry rates by state \# of establishments - harder
		\item Normalize net job creation by state employment
	\end{itemize}
	\item DONE - Aggregate from the bottom up using Compustat 
	\begin{itemize}
		\item Below are the results from the first version of this aggregation. The estimates are all in the right direction but not really significant. 
		\item This could be because my measure of R\&D is very noisy. Could improve by averaging weight from patent stuff with weight from compustat according to some parameter. How to do this without data mining?
	\end{itemize}
	\item LOOK AT THE DATA now! Yay, visualization! But with Stata...unless there's some way to send the results of my regressions to R in a convenient format...look this up. Maybe even \texttt{-estout-} has this!  
	\item Try not doing things in logs...
\end{enumerate}


\section{Results}
Note: All regressions below use state- and time-fixed effects. Their coefficients are omitted. 
\subsection{Total R\&D}
\subsubsection{Establishment Entry}
%\begin{landscape}
\begin{table}[h!]
	\caption{log-log OLS of Estab. Entry Rate / \# Estabs on R\&D / GDP and lags}
	\center
	\input{../Tables/totalGDP_e_entry_n_OLS_compustatAggregation.tex}
\end{table}
%\end{landscape}

\newpage
\begin{table}[h!]
	\caption{log-log OLS Estab. Entry Rate / \# Estabs on R\&D effective user cost of R\&D}
	\center
	\input{../Tables/totalGDP_e_entry_n_reduced_compustatAggregation.tex}
\end{table}

\begin{table}[h!]
	\caption{log-log IV Estab. Entry Rate / \# Estabs on R\&D by GDP, with effective user cost of R\&D as instrument}
	\center
	\input{../Tables/totalGDP_e_entry_n_IV_compustatAggregation.tex}
\end{table}

\begin{table}[h!]
	\caption{OLS log of R\&D / GDP on effective user cost of R\&D}
	\center
	\input{../Tables/totalGDP_firststage_compustatAggregation.tex}
\end{table}

\clearpage
\subsubsection{Net job creation by new firms}
\begin{table}[h]
	\caption{log-log OLS of Job Creation by Entrants / Total Employment on R\&D / GDP and lags}
	\center
	\input{../Tables/totalGDP_n_j_cr_n_OLS_compustatAggregation.tex}
\end{table}

\begin{table}[h]
	\caption{log-log OLS Job Creation by Entrants / Total Employment on R\&D effective user cost of R\&D}
	\center
	\input{../Tables/totalGDP_n_j_cr_n_reduced_compustatAggregation.tex}
\end{table}

\begin{table}[h]
	\caption{log-log IV Job Creation by Entrants / Total Employment on R\&D by GDP, with effective user cost of R\&D as instrument}
	\center
	\input{../Tables/totalGDP_n_j_cr_n_IV_compustatAggregation.tex}
\end{table}

\begin{table}[h!]
	\caption{OLS log of R\&D / GDP on effective user cost of R\&D}
	\center
	\input{../Tables/totalGDP_firststage_compustatAggregation.tex}
\end{table}

\clearpage
\subsection{Private R\&D}
\subsubsection{Establishment Entry}

\begin{table}[h]
	\caption{log-log OLS of Estab. Entry Rate / \# Estabs on R\&D / GDP and lags}
	\center
	\input{../Tables/privateGDP_e_entry_n_OLS_compustatAggregation.tex}
\end{table}

\begin{table}[h!]
	\caption{log-log OLS Estab. Entry Rate / \# Estabs on R\&D effective user cost of R\&D}
	\center
	\input{../Tables/privateGDP_e_entry_n_reduced_compustatAggregation.tex}
\end{table}

\begin{table}[h!]
	\caption{log-log IV Estab. Entry Rate / \# Estabs on R\&D by GDP, with effective user cost of R\&D as instrument}
	\center	
	\input{../Tables/privateGDP_e_entry_n_IV_compustatAggregation.tex}
\end{table}

\begin{table}[h]
	\caption{OLS log of R\&D / GDP on effective user cost of R\&D}
	\center
	\input{../Tables/privateGDP_firststage_compustatAggregation.tex}
\end{table}

\clearpage
\subsubsection{Net job creation by new firms}
\begin{table}[h!]
	\caption{log-log OLS of Job Creation by Entrants / Total Employment on R\&D / GDP and lags}
	\center
	\input{../Tables/privateGDP_n_j_cr_n_OLS_compustatAggregation.tex}
\end{table}

\begin{table}[h]
	\caption{log-log OLS Job Creation by Entrants / Total Employment on R\&D effective user cost of R\&D}
	\center
	\input{../Tables/privateGDP_n_j_cr_n_reduced_compustatAggregation.tex}
\end{table}

\begin{table}[h]
	\caption{log-log IV Job Creation by Entrants / Total Employment on R\&D by GDP, with effective user cost of R\&D as instrument}
	\center
	\input{../Tables/privateGDP_n_j_cr_n_IV_compustatAggregation.tex}
\end{table}

\begin{table}[h]
	\caption{OLS log of R\&D / GDP on effective user cost of R\&D}
	\center
	\input{../Tables/privateGDP_firststage_compustatAggregation.tex}
\end{table}



\end{document}